Multi-fluids for Representing Sub-\change[HW]{filter}{grid}-scale Convection

### 2020-07-16 submit3/manuscript.tex
Hilary's first complete draft of responses to 2nd reviewer comments

\title{Multi-fluids for Representing Sub-filter-scale Convection}

@@

\begin{abstract}
Multi-fluid modeling is a promising new method of representing sub- and near-grid-scale convection allowing for consistent and accurate
treatment of net mass transport by convection and of non-equilibrium dynamics . The air is partitioned into two or more
fluids which may represent, for example, updrafts and the stable environment. Each fluid has its own velocity, temperature and constituents
with separate equations of motion.

This paper presents two-fluid Boussinesq equations for representing under-resolved dry convection
with sinking and $w=0$ air in fluid 0 and rising air in fluid 1. A model for entrainment
and detrainment based on divergence  leads to excellent representation of the convective area fraction.
Previous multi-fluid modeling of convection has
used the same pressure for both fluids.
This is shown to be a bad approximation and  a model
for the pressure difference between the fluids based on divergence is presented.

Two vertical slice test cases are developed to tune parameters and to evaluate the two-fluid equations for representing dry, sub-grid-scale convection: a buoyant rising bubble and radiative convective equilibrium. These
are first simulated at high resolution and conditionally averaged based
on the sign of the vertical velocity. The test cases are next simulated with the two-fluid model which  reproduces
the mean properties of the rising and falling fluids in one column. 
\end{abstract}

\section*{Plain Language Summary}
Clouds and buoyant convection are often smaller than the grid size in weather and climate prediction models but they are of central importance. Therefore their effects are parameterized -- their interactions with the larger scales are estimated based on properties of the larger scales. Convection parameterizations are a large source of error in models of the atmosphere despite decades of effort to improve them. 
Some unrealistic assumptions remain such as that convection does not transport mass upwards, convection is in equilibrium with the surroundings and that the variations in the horizontal direction are not relevant. These make
it much simpler to incorporate convection parameterizations into existing models. 
Multi-fluid modeling
does not rely on these assumptions
but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model. This paper provides some closures necessary for multi-fluid modeling and evaluation of the technique for two dimensional dry convection.

@@

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
over to the Boussinesq equations because convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Boussinesq equations. Therefore, the Boussinesq equations without background stratification are chosen for simplicity:
\begin{eqnarray}
\frac{\partial \mathbf{u}}{\partial t} + \nabla\cdot(\mathbf{u}\mathbf{u})
+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
\label{eq:singleMom}
\\
\frac{\partial b}{\partial t} + \nabla\cdot(\mathbf{u}b)
 & = & \alpha\nabla^{2}b
\label{eq:singleb}
\\
\nabla\cdot\mathbf{u} & = & 0
\label{eq:singleDivFree}
\end{eqnarray}
where variables are defined in table \ref{tab:defns}. Note that the \add[HW]{Boussinesq} pressure \add[HW]{potential}, $P$, is actually pressure divided by a constant reference density\add[HW]{ and is referred to as just the pressure when considering the Boussinesq equations}.
\add[HW]{The pressure variations are determined up to a constant in order to ensure the divergence free constraint.}

@@

To derive a transport equation for $\sigma_i$, (\ref{eq:LagrangianLabel}) is combined with $I_i$ times (\ref{eq:singleDivFree}) and volume averaged. 
It is necessary to assume that operators permute with the averaging \cite<as described by>{TWV+18}. \add[HW]{Terms that appear because the averaging does not commute with the operators can be included in the transfers between fluids} \remove[HW]{Transfers between fluids are included at this stage} \add[HW]{which take the form}:
\begin{equation}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i}  =  \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\}
\label{eq:sigma}
\end{equation}
where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$.

Next the conditional averaging of terms in the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations is considered. Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
\begin{eqnarray}
\overline{I_i \nabla \cdot (\mathbf{u} \mathbf{u})} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
\overline{I_i \nabla (\mathbf{u} b)} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
\label{eq:filterAdvection}
\end{eqnarray}
The sub-filter-scale fluxes are represented by constant viscosity diffusion terms for each fluid. The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialized to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
\begin{eqnarray}
\overline{I_i \nu \nabla^2 \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
\overline{I_i \alpha \nabla^2 b} &\approx& \sigma_i \alpha \nabla^2b_i .
\end{eqnarray} 
%
The \add[HW]{Boussinesq} pressure \add[HW]{potetials} within each fluid are defined as:
\begin{equation}
\sigma_i P_i = \overline{I_i P}.
\end{equation}
The pressure gradient can then be decomposed as:
\begin{equation}
\overline{I_i \nabla P} = \sigma_i \nabla P_i + 
    \left[ P_i\nabla\sigma_i - \overline{P\nabla I_i} \right]
\end{equation}
The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using resolved variables and the full resolved version of the same force, both of which are related to drag. They will be represented by a drag, $\mathbf{D}_{ij}$. However this drag is likely to be smaller than the drag that is used, for example, in multi-phase modeling \cite<e.g.>{GBB+07} as it is representing the difference between two representations of drag, rather than the whole drag. Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.

Combining all terms gives the conditionally averaged momentum and buoyancy equations:
\begin{eqnarray}
\frac{\partial\sigma_i\mathbf{u}_{i}}{\partial t} + 
\nabla\cdot(\sigma_i \mathbf{u}_{i} \mathbf{u}_{i})
+ \sigma_i \nabla P_{i}
& = &
\sigma_i b_{i}\mathbf{k}
+
\nu\sigma_i\nabla^{2}\mathbf{u}_{i}
+
\sum_{j\ne i}\left\{
     \sigma_{j} S_{ji}\mathbf{u}_{ji}^{T}
   - \sigma_{i} S_{ij}\mathbf{u}_{ij}^{T}
   - \sigma_{i}\mathbf{D}_{ij}\right\}
\label{eq:momFlux}\\
\frac{\partial\sigma_i b_{i}}{\partial t} + 
\nabla\cdot(\sigma_i \mathbf{u}_{i} b_{i})
& = &
\alpha\sigma_i\nabla^{2}b_{i}
+
\sum_{j\ne i}\left\{
    \sigma_{j} S_{ji} b_{ji}^{T}
  - \sigma_{i} S_{ij} b_{ij}^{T}
\right\}.
\label{eq:bFlux}
\end{eqnarray}
These equations include mass transfers between fluids with $\mathbf{u}_{ij}^T$ being the velocity of the fluid transferred from $i$ to $j$ and $b_{ij}^T$ being the buoyancy of the fluid transferred from $i$ to $j$.

Equations (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated: 
\begin{eqnarray}
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i}
& = &
b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\}
\label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt}
& = &
\alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}
\end{eqnarray}
where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$,

@@

In order to derive a suitable form of parameterization for $p_i$ we will first consider the \citeA{BN86} model of multi-phase flow.

@@

\citeA{TEB19} stabilized the multi-fluid equations by adding a diffusion
term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
If a fluid perturbation pressure is set to $p_i=-\nu\partial w/\partial z$
then this is equivalent to the diffusion term in one dimension. However adding an artificial diffusion term will harm three dimensional simulations of
resolved convection in the free troposphere whereas adding a fluid
perturbation pressure will not. Inspired by both \citeA{BN86} and
\citeA{TEB19}
and obeying the constraints given above, the pressure in each fluid is chosen to be:
\begin{equation}
p_{i}=
-\underbrace{\gamma\nabla\cdot\mathbf{u}_{i}}_{\text{stabilization}}
+
\underbrace{\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j}_{\text{correction}}
\label{eq:Pi_div}
\end{equation}
where $\gamma$ is a compressibility with units $\text{m}^2 \text{s}^{-1}$. The ``stabilization'' term reduces to that of \protect{\citeA{TEB19}} in one dimension and the ``correction'' term ensures that $\sum_i \sigma_i p_i =0$. It should be noted that this parameterization destroys \add[HW]{exact} energy conservation. \add[HW]{In future work solving the compressible equations we plan to re-insert the energy lost due to this stabilization as heat.}

@@

It is useful to compare the transfer terms, $S_{ij}$, with models of entrainment, $\varepsilon$, and detrainment, $\delta$ used in convection parameterizations. If fluid 0 is the environment and fluid 1 is updrafts then the relationship is:
\begin{equation}
S_{01} = w_1\varepsilon, \;\;\;\;\;\;\;
S_{10} = w_0\delta.
\end{equation}
Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}. The first is similar to

the dynamic entrainment described by
\citeA{HC51}, \citeA{AK67} and \citeA{DBF+13}:
\begin{equation}
S_{ij}=\begin{cases}
-\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
0 & \text{otherwise.}
\end{cases}
\label{eq:Sdiv}
\end{equation}
This formulation prevents one fluid from accumulating when a fluid decelerates (at the top of a rising plume or at the bottom of descending air). {A} common form of lateral entrainment \cite<e.g.>{DBF+13} is also tested in section {\protect\ref{sec:results}}:
\begin{equation}
\varepsilon=\frac{0.2}{r_{c}}
\label{eq:fracEnt}
\end{equation}
where $r_{c}$ is the cloud or plume radius.

@@

The two fluid model is used to simulate the RCE test case in one
column of 40 cells with zero buoyancy gradient at the top and a buoyancy
gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
and uniform radiative cooling. The two fluids are initialized using
the time mean conditional horizontal averages from the single-fluid
resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
is used for all simulations to account for transfers throughout the
domain to represent cloud base mass flux (at the bottom boundary),
cloud top detrainment and lateral entrainment. $\gamma$ is set from
equation (\ref{eq:gammaDimAnal}) using the depth of the high resolution solution super adiabatic
layer as the length scale ($L=800\text{m}$) and the buoyancy scale
$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. (Scale analysis or boundary layer parameterization could instead be used to estimate $L$ independently.)
A simulation using
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
is shown in the top row of figure \ref{fig:RCE_singleColumn}.
The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
at about 0.5 throughout the depth, as in the resolved simulation,
with entrainment in the lower half of the domain ($S_{01}>0$) and
detrainment in the upper half ($S_{10}>0$), where the air decelerates
towards the top. The one column model reproduces the super-adiabatic
layer near the ground and the near uniform buoyancy away from the
ground but the buoyancy difference between the fluids is too large.
The updraft and downdraft velocities are captured well. The pressure
differences between fluids are too large which is consistent with
the over estimated buoyancy difference between fluids.

>>>>

\title{Multi-fluids for Representing Sub-\change[HW]{filter}{grid}-scale Convection}

@@

\begin{abstract}
\add[HW]{Traditional parameterizations of convection are a large source of error in weather and climate prediction models and the assumptions behind them are worse as resolution increases.}
Multi-fluid modeling is a promising new method of representing sub- and near-grid-scale convection allowing for \remove[HW]{consistent and accurate
treatment of} net mass transport by convection and \remove[HW]{of} non-equilibrium dynamics. The air is partitioned into two or more
fluids which may represent, for example, updrafts and the \change[HW]{stable}{non-updraft} environment. Each fluid has its own velocity, temperature and constituents with separate equations of motion.

This paper presents two-fluid Boussinesq equations for representing \change[HW]{under-resolved}{sub-grid-scale} dry convection with sinking and $w=0$ air in fluid 0 and rising air in fluid 1. Two vertical slice test cases are developed to tune parameters and to evaluate the two-fluid equations: a buoyant rising bubble and radiative convective equilibrium. These
are first simulated at high resolution \add[HW]{with a single-fluid model} and conditionally averaged based
on the sign of the vertical velocity. The test cases are next simulated with the two-fluid model \remove[HW]{which reproduces
the mean properties of the rising and falling fluids} in one column. 
A model for entrainment and detrainment based on divergence  leads to excellent representation of the convective area fraction. Previous multi-fluid modeling of convection has used the same pressure for both fluids. This is shown to be a bad approximation and  a model for the pressure difference between the fluids based on divergence is presented. 
\end{abstract}

\section*{Plain Language Summary}
Clouds and buoyant convection are often smaller than the grid size in weather and climate prediction models but they are of central importance. Therefore their effects are parameterized -- their interactions with the larger scales are estimated based on properties of the larger scales. Convection parameterizations are a large source of error in models of the atmosphere despite decades of effort to improve them. 
Some unrealistic assumptions remain such as that convection does not transport mass upwards, convection is in equilibrium with the surroundings and that the variations in the horizontal direction are not relevant. These make
it much simpler to incorporate convection parameterizations into existing models.Multi-fluid modeling does not rely on these assumptions
but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model. This paper provides some closures necessary for multi-fluid modeling and evaluation of the technique for two dimensional dry convection.

@@

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
over to the Boussinesq equations because convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Boussinesq equations. Therefore, the Boussinesq equations without background stratification are chosen for simplicity:
\begin{eqnarray}
\frac{\partial \mathbf{u}}{\partial t} + \nabla\cdot(\mathbf{u}\mathbf{u})
+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
\label{eq:singleMom}
\\
\frac{\partial b}{\partial t} + \nabla\cdot(\mathbf{u}b)
 & = & \alpha\nabla^{2}b
\label{eq:singleb}
\\
\nabla\cdot\mathbf{u} & = & 0
\label{eq:singleDivFree}
\end{eqnarray}
where variables are defined in table \ref{tab:defns}. Note that the \add[HW]{Boussinesq} pressure \add[HW]{potential}, $P$, is actually pressure divided by a constant reference density\add[HW]{ and is referred to as just the pressure when considering the Boussinesq equations}.
\add[HW]{The pressure variations are determined up to a constant in order to ensure that the velocity is divergence free.}

@@

To derive a transport equation for $\sigma_i$, (\ref{eq:LagrangianLabel}) is combined with $I_i$ times (\ref{eq:singleDivFree}) and volume averaged. 
It is necessary to assume that operators permute with the averaging \cite<as described by>{TWV+18}. \add[HW]{Terms that appear because the averaging does not commute with the operators can be included in the transfers between fluids.} \remove[HW]{Transfers between fluids are included at this stage} \add[HW]{The equation for $\sigma_i$ is then}:
\begin{equation}
\frac{\partial\sigma_{i}}{\partial t}+\nabla\cdot\sigma_{i}\mathbf{u}_{i}  =  \sum_{j\ne i}\left\{ \sigma_{j}S_{ji}-\sigma_{i}S_{ij}\right\}
\label{eq:sigma}
\end{equation}
where $\sigma_{i}S_{ij}$ is the transfer rate from fluid $i$ to $j$.

Next the conditional averaging of terms in the momentum (\ref{eq:singleMom}) and buoyancy (\ref{eq:singleb}) equations is considered. \add[HW]{The filter scale is assumed to be equal to the grid scale but the derivation does not rely on this.} Conditionally averaging the advection terms leads to sub-filter-scale fluxes, $F_{SF}$, since the velocity and buoyancy are not uniform within each fluid at the filter scale:
\begin{eqnarray}
\overline{I_i \nabla \cdot (\mathbf{u} \mathbf{u})} &=& \nabla \cdot (\sigma_i \mathbf{u}_i  \mathbf{u}_i) + F_\text{SF}^{\mathbf{u}_i} \\
\overline{I_i \nabla (\mathbf{u} b)} &=&  \nabla \cdot (\sigma_i \mathbf{u}_i b_i) + F_\text{SF}^{b_i}
\label{eq:filterAdvection}
\end{eqnarray}
The sub-filter-scale fluxes are represented by constant viscosity diffusion terms for each fluid. The diffusion terms are written so that, in the absence of transfers between fluids and if both fluids are initialized to be identical, the fluids remain identical and $\sigma_i$ acts as a passive tracer:
\begin{eqnarray}
\overline{I_i \nu \nabla^2 \mathbf{u}} &\approx& \sigma_i \nu \nabla^2 \mathbf{u}_i \\
\overline{I_i \alpha \nabla^2 b} &\approx& \sigma_i \alpha \nabla^2b_i .
\end{eqnarray} 
%
The \add[HW]{Boussinesq} pressure \add[HW]{potetials} within each fluid are defined as:
\begin{equation}
\sigma_i P_i = \overline{I_i P}.
\end{equation}
The pressure gradient can then be decomposed as:
\begin{equation}
\overline{I_i \nabla P} = \sigma_i \nabla P_i + 
    \left[ P_i\nabla\sigma_i - \overline{P\nabla I_i} \right]
\end{equation}
The terms in square brackets are the difference between the pressure force pushing outward from the fluid calculated using resolved variables and the full resolved version of the same force, both of which are related to drag. They will be represented by a drag, $\mathbf{D}_{ij}$. However this drag is likely to be smaller than the drag that is used, for example, in multi-phase modeling \cite<e.g.>{GBB+07} as it is representing the difference between two representations of drag, rather than the whole drag. Sensitivity to $\mathbf{D}_{ij}$ will be investigated in section \ref{sec:results}.

Combining all terms gives the conditionally averaged momentum and buoyancy equations:
\begin{eqnarray}
\frac{\partial\sigma_i\mathbf{u}_{i}}{\partial t} + 
\nabla\cdot(\sigma_i \mathbf{u}_{i} \mathbf{u}_{i})
+ \sigma_i \nabla P_{i}
& = &
\sigma_i b_{i}\mathbf{k}
+
\nu\sigma_i\nabla^{2}\mathbf{u}_{i}
+
\sum_{j\ne i}\left\{
     \sigma_{j} S_{ji}\mathbf{u}_{ji}^{T}
   - \sigma_{i} S_{ij}\mathbf{u}_{ij}^{T}
   - \sigma_{i}\mathbf{D}_{ij}\right\}
\label{eq:momFlux}\\
\frac{\partial\sigma_i b_{i}}{\partial t} + 
\nabla\cdot(\sigma_i \mathbf{u}_{i} b_{i})
& = &
\alpha\sigma_i\nabla^{2}b_{i}
+
\sum_{j\ne i}\left\{
    \sigma_{j} S_{ji} b_{ji}^{T}
  - \sigma_{i} S_{ij} b_{ij}^{T}
\right\}.
\label{eq:bFlux}
\end{eqnarray}
These equations include mass transfers between fluids with $\mathbf{u}_{ij}^T$ being the velocity of the fluid transferred from $i$ to $j$ and $b_{ij}^T$ being the buoyancy of the fluid transferred from $i$ to $j$. 
Equations (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated: 
\begin{eqnarray}
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i}
& = &
b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\}
\label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt}
& = &
\alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}
\end{eqnarray}
where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$.

@@

In order to derive a suitable form of \change[HW]{parameterization}{model} for $p_i$ we will first consider the \citeA{BN86} model of multi-phase flow.

@@

\citeA{TEB19} stabilized the multi-fluid equations by adding a diffusion
term $\nu\partial w^{2}/\partial z^{2}$ to the RHS of the $w$ equation.
If a fluid perturbation pressure is set to $p_i=-\nu\partial w/\partial z$
then this is equivalent to the diffusion term in one dimension. However adding an artificial diffusion term will harm three dimensional simulations of
resolved convection in the free troposphere whereas adding a fluid
perturbation pressure will not. Inspired by both \citeA{BN86} and
\citeA{TEB19}
and obeying the constraints given above, the pressure in each fluid is chosen to be:
\begin{equation}
p_{i}=
-\underbrace{\gamma\nabla\cdot\mathbf{u}_{i}}_{\text{stabilization}}
+
\underbrace{\gamma\sum_j \sigma_j\nabla\cdot\mathbf{u}_j}_{\text{correction}}
\label{eq:Pi_div}
\end{equation}
where $\gamma$ is a compressibility with units $\text{m}^2 \text{s}^{-1}$. The ``stabilization'' term reduces to that of \protect{\citeA{TEB19}} in one dimension and the ``correction'' term ensures that $\sum_i \sigma_i p_i =0$. It should be noted that this parameterization destroys \add[HW]{exact} energy conservation. \add[HW]{In future work solving the compressible equations we plan to re-insert the energy lost due to this stabilization as turbulent kinetic energy and heat.}

@@

It is useful to compare the transfer terms, $S_{ij}$, with models of entrainment, $\varepsilon$, and detrainment, $\delta$ used in convection parameterizations. If fluid 0 is the environment and fluid 1 is updrafts then the relationship is:
\begin{equation}
S_{01} = w_1\varepsilon, \;\;\;\;\;\;\;
S_{10} = w_0\delta.
\end{equation}
Results using two formulations of entrainment are presented in section {\protect\ref{sec:results}}. The first is similar to the dynamic entrainment described by \citeA{HC51}, \citeA{AK67} and \citeA{DBF+13}:
\begin{equation}
S_{ij}=\begin{cases}
-\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
0 & \text{otherwise.}
\end{cases}
\label{eq:Sdiv}
\end{equation}
This formulation prevents one fluid from accumulating when a fluid decelerates (at the top of a rising plume or at the bottom of descending air). {A} common form of lateral entrainment \cite<e.g.>{DBF+13} is also tested in section {\protect\ref{sec:results}}:
\begin{equation}
\varepsilon=\frac{0.2}{r_{c}}
\label{eq:fracEnt}
\end{equation}
where $r_{c}$ is the cloud or plume radius.

@@

The two fluid model is used to simulate the RCE test case in one
column of 40 cells with zero buoyancy gradient at the top and a buoyancy
gradient of $10^{-5}\text{s}^{-2}$ at the ground for both fluids
and uniform radiative cooling. The two fluids are initialized using
the time mean conditional horizontal averages from the single-fluid
resolved simulation. The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
is used for all simulations to account for transfers throughout the
domain to represent cloud base mass flux (at the bottom boundary),
cloud top detrainment and lateral entrainment. $\gamma$ is set from
equation (\ref{eq:gammaDimAnal}) using the depth of the high resolution solution super adiabatic
layer as the length scale ($L=800\text{m}$) and the buoyancy scale
$B=L\ \partial b/\partial z=8\times10^{-3}\text{m}\text{s}^{-2}$
giving $\gamma=2000\text{m}^{2}\text{s}^{-1}$. \add[HW]{(If scale analysis is used to estimate $L$ and $B$, values within a factor of 10 are calculated, depending on the assumptions.)}
A simulation using
$S_{ij}=-\nabla\cdot\mathbf{u}_{i}$, no drag and $b_{ij}^{T}=b_{i}$
is shown in the top row of figure \ref{fig:RCE_singleColumn}.
The entrainment model $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ keeps $\sigma_{i}$
at about 0.5 throughout the depth, as in the resolved simulation,
with entrainment in the lower half of the domain ($S_{01}>0$) and
detrainment in the upper half ($S_{10}>0$), where the air decelerates
towards the top. The one column model reproduces the super-adiabatic
layer near the ground and the near uniform buoyancy away from the
ground but the buoyancy difference between the fluids is too large.
The updraft and downdraft velocities are captured well. The pressure
differences between fluids are too large which is consistent with
the over estimated buoyancy difference between fluids.
